MSc Statistical overview

### 2018-01-27 MScFigures_noGather.Rmd
Add files via upload

  * File creation date: `r Sys.Date()`
  * `r R.version.string`
  * `tidyverse` package version: `r packageVersion("tidyverse")`
  * `lme4` package version `r packageVersion("lme4")`
  * `MASS` package version `r packageVersion("MASS")`
  * `MuMIn` package version `r packageVersion("MuMIn")`
  * `emmeans` package version `r packageVersion("emmeans")`
  * `boot` package version `r packageVersion("boot")`
  * `brms` package version `r packageVersion("brms")`
  * `loo` package version `r packageVersion("loo")`
  * `fitdistrplus` package version `r packageVersion("fitdistrplus")`
  * `mefa` package version `r packageVersion("mefa")`
  * `library(devtools)` and `install_github("vqv/ggbiplot")` package version `r packageVersion("ggbiplot")`
  * also requires [rtools](https://cran.r-project.org/bin/windows/Rtools/)

@@

```{r Load_packages and functions, message=FALSE, warning=FALSE}
library(tidyverse)
library(lme4)
library(MASS)
library(MuMIn)
library(emmeans)
library(boot)
library(brms)
library(loo)
library(fitdistrplus)
library(mefa)
library(ggbiplot)

@@

#### Gather ####
length(unique(fdata$indiv2))
Cross<- data.frame(c(rep(1:100, times=225)))
fdatac <- cbind(fdata,Cross)
colnames(fdatac)[11]<-"cross"
fdatac %>% gather(Trait, Value, c(4,6,7)) -> fdata_gather # The warning is an inconsequential bug from tidyverse (https://github.com/tidyverse/tidyr/issues/386)
fdata_gather$Value<-as.numeric(fdata_gather$Value)
fdata_gather$Trait<-as.factor(fdata_gather$Trait)
fdata_gather <- fdata_gather[,-c(2:4)]
```

@@

Co-occurence with gather: what is the difference? 
Here I want to see that the traits are associating differently at every cross for each indiv

````{r Co-occurence model GATHER}

baysianGLMERmyc_lesion_GTHR <- brm(Value ~ Trait * species + (1|pop) + (1|indiv2/cross), data = fdata_gather, family = bernoulli,control = list(adapt_delta = 0.95))

summary(baysianGLMERmyc_lesion_GTHR)
bayes_R2(baysianGLMERmyc_lesion_GTHR)

baysianGLMERmyc_lesion_GTHR_1 <- brm(Value ~ Trait * location * species + (1|pop) + (1|indiv2/cross), data = fdata_gather, family = bernoulli,control = list(adapt_delta = 0.95))

baysianGLMERmyc_lesion_GTHR_2 <- brm(Value ~ Trait + (1|pop) + (1|indiv2/cross), data = fdata_gather, family = bernoulli,control = list(adapt_delta = 0.95))

baysianGLMERmyc_lesion_GTHR_NULL <- brm(Value ~ 1 + (1|pop) + (1|indiv2/cross), data = fdata_gather, family = bernoulli,control = list(adapt_delta = 0.95))

model.sel(baysianGLMERmyc_lesion_GTHR,baysianGLMERmyc_lesion_GTHR_1,baysianGLMERmyc_lesion_GTHR_2,baysianGLMERmyc_lesion_GTHR_NULL) #not sure if this function will work with brm model, if not ill just have to do a waic and then a compare like the previous... should test with a smaller model
```
**SUMMARY:**

What is significant with the correlation~location*sp model?

What does it change when we gather the model? What am I really testing?
Does it really test what I want it to test?

What is significant when we gather? Is this model even any good?

>>>>

  * File creation date: `r Sys.Date()`
  * `r R.version.string`
  * `tidyverse` package version: `r packageVersion("tidyverse")`
  * `lme4` package version `r packageVersion("lme4")`
  * `MASS` package version `r packageVersion("MASS")`
  * `MuMIn` package version `r packageVersion("MuMIn")`
  * `emmeans` package version `r packageVersion("emmeans")`
  * `boot` package version `r packageVersion("boot")`
  * `brms` package version `r packageVersion("brms")`
  * `loo` package version `r packageVersion("loo")`
  * `fitdistrplus` package version `r packageVersion("fitdistrplus")`

@@

```{r Load_packages and functions, message=FALSE, warning=FALSE}
library(tidyverse)
library(lme4)
library(MASS)
library(MuMIn)
library(emmeans)
library(boot)
library(brms)
library(loo)
library(fitdistrplus)

@@

#### Gather ####
length(unique(fdata$indiv2))
Cross<- data.frame(c(rep(1:100, times=225)))
fdatac <- cbind(fdata,Cross)
colnames(fdatac)[11]<-"cross"
fdatac %>% gather(Trait, Value, c(4,6,7)) -> fdata_gather # The warning is an inconsequential bug from tidyverse (https://github.com/tidyverse/tidyr/issues/386)
fdata_gather$Value<-as.numeric(fdata_gather$Value)
fdata_gather$Trait<-as.factor(fdata_gather$Trait)
fdata_gather <- fdata_gather[,-c(2:4)]
write.csv(fdata_gather, "fdata_gather.csv")
```

@@
